\documentclass{article}

\usepackage[affil-it]{authblk}

\usepackage[USenglish,american]{babel}
\usepackage[pdftex]{graphicx}
\usepackage{epstopdf}

\usepackage{cite}

\usepackage{amsfonts,amsmath,amsthm,amssymb}

\usepackage{tikz,pgf}
\usetikzlibrary{fit}

\usepackage{csvsimple}

%\pagestyle{empty}
\setlength{\parindent}{0mm}
\usepackage[letterpaper, margin=1in]{geometry}
%\usepackage{showframe}

\usepackage{multicol}
\usepackage{enumerate}

\usepackage{verbatim}
\usepackage{listings}

\usepackage{color}

%%
%% Julia definition (c) 2014 Jubobs
%%
\lstdefinelanguage{Julia}%
  {morekeywords={abstract,break,case,catch,const,continue,do,else,elseif,%
      end,export,false,for,function,immutable,import,importall,if,in,%
      macro,module,otherwise,quote,return,switch,true,try,type,typealias,%
      using,while},%
   sensitive=true,%
   alsoother={$},%
   morecomment=[l]\#,%
   morecomment=[n]{\#=}{=\#},%
   morestring=[s]{"}{"},%
   morestring=[m]{'}{'},%
}[keywords,comments,strings]%

\lstset{%
    language         = Python,
    basicstyle       = \footnotesize\ttfamily,,
    keywordstyle     = \bfseries\color{blue},
    stringstyle      = \color{magenta},
    commentstyle     = \color{red},
    showstringspaces = false,
    backgroundcolor  = \color{lightgray},
    numbers          = left,
    title            = \lstname,
    numberstyle      = \tiny\color{lightgray}\ttfamily,
}

\usepackage{xspace}
\usepackage{url}
\usepackage{cite}

%\usepackage{titlesec}
%\titlespacing*{\subsubsection}{0pt}{*0}{*0}
%\titlespacing*{\subsection}{0pt}{0pt}{*0}
%\titlespacing*{\section}{0pt}{0pt}{*0}

\newcommand{\Bold}{\mathbf}

\setlength{\parskip}{1em}
%\setlength{\parindent}{1em}

\title{SME-Topic Modeling}
\date{\today}
\author{Philip Robinson}
\affil{NASA: Jet Propoultion Labratory}

\begin{document}

\maketitle

\begin{abstract}
  In a large commnity, enlisting of potential collaborators and subject matter experts
  greatly impacts the success of a project. Infering identification and ranking of
  these participants' relevent knowlege to a task or project is nessicary to develop
  impactful teams from these large communities\cite{Minto2007}. It is the goal of this
  paper to provide an outlined and strategy to infer best participants from their
  document contributions to a corpus. Topic modeling, such as BTM\cite{Yan2013}, LDA,
  and CTM, have long been used to group related topics\cite{Alghamdi2015}. Likewise,
  author modeling has been used to measure attribution\cite{Rexha2018} and
  contribution\cite{AldebeiHJ016}. Author-Topic modeling establishes strategy to
  relate topics to authors\cite{Rosen-Zvi2004}. Under the, common, assumption that
  authorship implies relevent knowlege to a document's topic; proposed is to explore
  the space of Author-Topic modeling as a mechanism for measuring expertise against a
  project description, as a query.
\end{abstract}

% http://www.sfp.caltech.edu/students/proposal/other_project_plans
% https://trs.jpl.nasa.gov/

\section{Introduction}

For my JPL fellowship I will be exploring Subject Matter Expert (SME) retrieval,
from a collection of documents with attribution. SME retrieval is nessicary for
building effective teams for specific projects. In order to support the scale of an
institution like JPL/NASA, and at the complexity of the problems they address, we are
interested in strategies to infer and retrieve SMEs. An effective SME retrieval program
would significantly reduce coordination overhead of election and discovery of
contributors to complex, domain specific, problems.

JPL's \texttt{A-Team} explored, then developed, a now existing SME retrieval program.
In developing this program, teams cited work on heirarchical clustering by
frequent-itemsets\cite{wang2003,kiran2010}. Frequent-itemsets\cite{Agrawal1993} are a
tool from relation mining, which has historically been used to discover hidden
subpopulations with a shared characteristic pool. Clustering by frequent-itemsets has the
advantage of supporting relatively small document sizes, and of varying shape. This is
partly because items for itemsets are not weighted by TF or IDF, but rather simply
their existance in a document and a support parameter.

\section{Objectives}

The goal of this project is to propose an alternative, or collaborative, strategy for
SME retrieval. The document set will be different from \texttt{A-Team} set, although
not distinct. Ideally, this should also serve as a bases for clustering document
resources in preperation for such projects.

\section{Approach}

I am interested in author-topic\cite{Rosen-Zvi2004} modeling (ATM) to address the problem of
SME retrieval. The base algorithm for ATM is an extension of LDA to include modeling authors
of documents. A query system would then be developed to rank Author-topics against project
descriptions and like documents.

There exists an open-source implementation of ATM in the \texttt{gensim}\cite{rehurek_lrec}
module for \texttt{python}. If this proves effective, I would like to explore derivatives
to ATM that rely on CTM instead of LDA. Unlike LDA, CTM models relationships
between topics as well. % There also exist CTM models that weigh feilds of a document differently
To my knowlege this strategy does not yet exist, and therefore adaptation may have high risk
effect on the timeline.

\section{Evaluation}

In order to evaluate our model, we will need to have training and test SME sets. In order
to establish these, I propose a test and training set split by bisecting by mincut\cite{Feige2002}
a graph where authors are verticies, and edges exist for each co-authors relationship.



\section{Schedule}


\begin{comment}

The \texttt{A-Team} currently has a proposed solution, XXX. I am tasked with providing a competing solution, that can learn from more general corpus. This will allow us to compare results in a useful way.

%\subsection{What is general technical area in which you will be working?}
%\subsection{What is the problem that you are trying to solve?}
%\subsection{How did this problem arise?}
%\subsection{Why is this problem interesting or worthwhile?}
\subsection{What is the status of related research by your mentor or group by the group that you will be joining?}
\subsection{What will be the contribution and significance of your effort?}

\section{Objectives}


\section{Materials}
\section{Results}
\section{Discussion}
\subsection{Study Assumptions}
\subsection{Data Acquisition}
\end{comment}

\bibliography{references.bib}{}
\bibliographystyle{plain}

\end{document}
